Analysis paper

### 2021-05-04 analysis/analysis.Rmd
save distrbution plot
add some plots for individual forecasters

ggsave(here("analysis", "plots", "daily_truth.png"))
```

@@

>>>>

ggsave(here("analysis", "plots", "daily_truth.png"))
```
## Number of expert forecasters

```{r num-forecasters, results = 'asis'}
dt <- crowdforecast_data[!(model %in% c("Crowd-Rt-Forecast",
                                        "EpiNow2_secondary", 
                                        "EpiExpert-ensemble", 
                                        "EpiNow2")), 
                         .(`number of forecasters` = length(unique(model))), , 
                         by = c("forecast_date", "location_name", "target_type")
][order(forecast_date)][
  !is.na(forecast_date)]

dt[, .(sd = sd(`number of forecasters`), 
                             mean = mean(`number of forecasters`), 
                             min  = min(`number of forecasters`), 
                             max = max(`number of forecasters`), 
                             median = median(`number of forecasters`)), 
   by = c("location_name", "target_type")]

```
```{r, results = 'asis'}
dt <- crowdforecast_data[!(model %in% c("Crowd-Rt-Forecast",
                                        "EpiNow2_secondary", 
                                        "EpiExpert-ensemble", 
                                        "EpiNow2")) & forecast_date %in% forecast_dates$unfiltered]

num_fc <- dt[, .(n_forecasts = length(unique(forecast_date))),
             by = c("model")][order(n_forecasts)]

num_fc %>%
  ggplot(aes(x = n_forecasts)) + 
  geom_bar() + 
  theme_light() + 
  labs(x = "Number of available submissions", 
       y = "Number of forecasters")

ggsave("plots/crowdforecast_regularity.png")

## Number of expert forecasters

```{r, results = 'asis'}

dt <- crowdforecast_data[!(model %in% c("Crowd-Rt-Forecast",
                                        "EpiNow2_secondary", 
                                        "EpiNow2")) & forecast_date %in% forecast_dates$unfiltered]

crowddata <- merge_pred_and_obs(dt, truth_data)

scores <- eval_forecasts(
  data = crowddata[grepl("2", target)],
  summarise_by = c("model", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "EpiExpert-ensemble"
)

plot_df <- merge(num_fc, scores, by = "model")

plot_df %>%
  ggplot(aes(y = scaled_rel_skill, x = n_forecasts)) + 
  geom_point() + 
  theme_light() + 
  facet_wrap(~ target_type) + 
  labs(y = "Scaled relative skill", x = "Number of available submissions") + 
  geom_smooth(method='lm', formula= y~x)

ggsave("plots/skill-vs-forecast-freq.png")

@@

ggsave("plots/distribution_scores.png")
